Data Migration under a Changing Schema

### 2023-07-10 2022Migration/articleMigrationFACS.tex
WIP on abstract

\title{Data Migration under a Changing Schema}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Sebastiaan Joosten\inst{1}\orcidID{0000-0002-6590-6220}\\ \and
Stef Joosten\inst{2,3}\orcidID{0000-0001-8308-0189}}
%
\authorrunning{S. Joosten}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Minnesota, Minneapolis, USA \and Open Universiteit Nederland, Heerlen, the Netherlands\\ 
\email{stef.joosten@ou.nl} \and
Ordina NV, Nieuwegein, the Netherlands}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Software generators can help to increase the frequency of releases and their reliability. They save on time spent on development and fixing human-induced mistakes by compiling a specification into a working information system. However, many generators do not support data migrations. Data migration is necessary when an incremental deployment changes the system's schema. Consequently, developers tend to avoid migrations or migrate data ``by hand''.

@@

This paper aims to preserve the semantics of data by satisfying concrete business requirements. The migration process is based on the assumption that software is deployed incrementally, the existing data set may be polluted, human interaction may be required, the meaning of data must be preserved, the business continues during the migration without interruption (zero downtime), and there is a compiler to generate an information system from a given schema. The correctness of the migration is the focus of this paper, while efficiency is outside its scope.

@@

\subsection{Data Migrations}
   Data migration occurs when a desired system replaces an existing one,
   while preserving the meaning of the present data as much as possible~\cite{Spivak2012}.
   %Just copying the set of data from the existing system to the desired system is obviously wrong if the schemas of both systems differ.
   %
   In practice, data migrations are done by deploying the desired system and the existing system side-by-side,
   while transferring data in a controlled fashion.
   Typically, a migration strategy (e.g. case by case, customer by customer, or in batches) is in place
   to ensure the preservation of valuable data and the quality of the migration.
   Automating this process completely is unrealistic in many cases:
   While smaller increments improve the chance that a fully automatic migration is possible, there will always be cases where human intervention is required.
   Manual interventions can be necessary to resolve data pollution, new business rules, or to fix known issues in the old system.
   Consequently, a migration engineer must have the freedom to tailor any automatic approach to migration to suit the particulars.

>>>>

\title{Data Migration under a Changing Schema}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Sebastiaan Joosten\inst{1}\orcidID{0000-0002-6590-6220}\\ \and
Stef Joosten\inst{2,3}\orcidID{0000-0001-8308-0189}}
%
\authorrunning{S. Joosten}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Minnesota, Minneapolis, USA \and Open Universiteit Nederland, Heerlen, the Netherlands\\ 
\email{stef.joosten@ou.nl} \and
Ordina NV, Nieuwegein, the Netherlands}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}  % There are 176 words in the abstract
Software generators can help to increase the frequency of releases and their reliability.
They save on time spent on development and fixing human-induced mistakes by compiling a specification into a working information system.
However, many generators do not support data migrations.
Data migration is necessary when an incremental deployment changes the system's schema.
Consequently, developers tend to avoid migrations or migrate data ``by hand''.

@@

This paper defines a migration process that preserves the semantics of data by means of rules (constraints).
The migration process is based assumptions and requirements that aim for a large class of data migrations in practice.
This paper focuses on correctness of the migration. Efficiency of the migration is outside its scope.

@@

\subsection{Data Migrations}
   Data migration occurs when a desired system replaces an existing one,
   while preserving the meaning of the present data as much as possible~\cite{Spivak2012}.
   %Just copying the set of data from the existing system to the desired system is obviously wrong if the schemas of both systems differ.
   %
   In practice, data migrations are done by deploying the desired system and the existing system side-by-side,
   while transferring data in a controlled fashion.
   Typically, a migration strategy (e.g. case by case, customer by customer, or in batches) is in place
   to ensure the preservation of valuable data and the quality of the migration.
   To fully automate every incremental data migration is unrealistic.
   Smaller increments stand a higher chance of being automated, but there will always be cases where some human intervention is required.
   Manual interventions can be necessary to resolve data pollution, new business rules, or to fix known issues in the old system.
   Consequently, a migration engineer must have the freedom to tailor any automatic approach to migration to suit the particulars.
